Implementation of a Fuzzy Rule-Based Classifier using Genetic Algorithms

### 2017-12-14 Article/article.tex
Adding the figures

\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
	urlcolor=red,
	linkcolor=red,
	colorlinks=red,
}

@@

(Do we have to do section X is for Y,....)

@@

@@

\subsection{Modeling the algorithm}

@@

\subsection{The fitness function}

According to the law of the fittest, the best individuals have more chance breeding and transmiting their genes. But what does it mean for an individual to be fit?\\
For this work, we define the fitness function as the accuracy of prediction of an individual given a test data.

\section{Implementation}

Optimization : cache individual rule fitnesses\\
Set of rules : may be rules that are incorrect

\section{Results and Conclusion}

@@

The calculation of the fitness function is the core of our implementation.\\
We will be trying to explain in depth the structure of that function.

\subsection{Vector of best class confidence}

@@

\[\mu_A=
min
\begin{pmatrix}
max(A(p(1),j),\forall j \in D(1))\\
\vdots \\
max(A(p(s),j),\forall j \in D(s))
\end{pmatrix}
    \]
\textbf{Example:}\\
\\
Let take our example rule:
\begin{center}
If Sepal Length is Small AND Sepal Width is Medium OR Big AND Petal Width is Small OR Medium OR Big
\end{center}
And a data instance (normalized): $x_1=0.97,x_2=0.86,x_3=0.97,x_4=0.88$.\\
\[
\begin{split}
\mu_A &= min
\begin{pmatrix}
max(\mu_S(0.97))\\
max(\mu_M(0.86),\mu_B(0.86))\\
max(\mu_S(0.88),\mu_M(0.88),\mu_B(0.88))
\end{pmatrix}\\
&= min
\begin{pmatrix}
max(0)\\
max(0.28,0.72)\\
max(0,0.24,0.76)
\end{pmatrix}\\
&= min(0,0.72,0.76) = 0
\end{split}
\]
\\
\begin{center} \rule[1ex]{.5\textwidth}{.5pt} \end{center}
\newpage

@@

We want now to get the predicted confidence of classes for an instance.\\
$\vec{Conf}$ gives us the fittest class for each rule, and $\vec{\mu_A}$ its confidence given an instance of data. \\
There is several way to compute the class predicted using these vectors.
\\
\\
\textbf{Simple method:}
\\
For each class, we take the average of $\mu_A$ for every rule that have that class as the highest truth degree:
\[
\text{Predicted Classes Confidence: }
\begin{pmatrix}
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_1\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_2\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_3
\end{pmatrix}
\]
Here, the class predicted will simply be the maximum average.

@@

The accuracy gives us the percentage of well predicted instances of our classification on a test data. We can use only this score as a fitness function.\\
It seems that using the training data to define the truth degree, then applying the simple method is already a good way to classify.\\
When taking the average of the average accuracy of 20 populations of 20 randomly generated individuals, we have a 0.77 accuracy.\\
And when taking the average accuracy of the fittest individual of 20 random populations, we get a 0.96 accuracy.\\
Decision Tree Classifier is a similar method with crisp rules. The accuracy of that method is 0.92 on the same dataset.\\
However, accuracy score is not our only concern : we would like to have the fewest rules as possible, as we want to produce a clear and simple rule system if one exists. So we have to compute a fitness function combining both the accuracy score and the complexity of the ruleset.
This is where we decided to change our fitness function for his way:

@@

\bibliography{GFL.bib}
\bibliographystyle{plain}
\end{document}

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{ {img/} }

\hypersetup{
	urlcolor=red,
	linkcolor=red,
	colorlinks=red,
}

@@

@@

\newpage

@@

\begin{figure}
\centering
\caption{The genetic fuzzy system we implemented}
\includegraphics[scale=0.5]{genefuzzy}
\end{figure}
\subsection{Modeling the algorithm}

\begin{figure}
\includegraphics[scale=0.5]{genealgo}
\centering
\caption{Decomposition of a genetic algorithm}
\end{figure}

@@

\newpage

@@

According to the law of the fittest, the best individuals have more chance breeding and transmitting their genes. But what does it mean for an individual to be fit?
The calculation of the fitness function is the core of our implementation.\\
We will be trying to explain in depth the structure of that function.
This figure represents how it works:\\

\begin{figure}
\centering
\caption{Finding the class confidences}
\includegraphics[scale=0.3]{fitnessfunct}
\end{figure}
\subsection{Vector of best class confidence}

@@

\[\mu_A=
min
\begin{pmatrix}
max(A(p(1),j),\forall j \in D(1))\\
\vdots \\
max(A(p(s),j),\forall j \in D(s))
\end{pmatrix}
    \]
\textbf{Example:}\\
\\
Let take our example rule:
\begin{center}
If Sepal Length is Small AND Sepal Width is Medium OR Big AND Petal Width is Small OR Medium OR Big
\end{center}
And a data instance (normalized): $x_1=0.97,x_2=0.86,x_3=0.97,x_4=0.88$.\\
\[
\begin{split}
\mu_A &= min
\begin{pmatrix}
max(\mu_S(0.97))\\
max(\mu_M(0.86),\mu_B(0.86))\\
max(\mu_S(0.88),\mu_M(0.88),\mu_B(0.88))
\end{pmatrix}\\
&= min
\begin{pmatrix}
max(0)\\
max(0.28,0.72)\\
max(0,0.24,0.76)
\end{pmatrix}\\
&= min(0,0.72,0.76) = 0
\end{split}
\]
\\

@@

We want now to get the predicted confidence of classes for an instance.\\
$\vec{Conf}$ gives us the fittest class for each rule, and $\vec{\mu_A}$ its confidence given an instance of data. \\
For each class, we take the average of $\mu_A$ for every rule that have that class as the highest truth degree:
\[
\text{Predicted Classes Confidence: }
\begin{pmatrix}
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_1\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_2\\
avg(\mu_A^k(r_i)), \forall & i & | & Conf(r_i)=C_3
\end{pmatrix}
\]
Here, the class predicted will simply be the maximum average.

@@

The accuracy gives us the percentage of well predicted instances of our classification on a test data. We can use only this score as a fitness function.\\
However, accuracy score is not our only concern : we would like to have the fewest rules as possible, as we want to produce a clear and simple rule system if one exists. So we have to compute a fitness function combining both the accuracy score and the complexity of the ruleset.
This is where we decided to change our fitness function for his way:

@@

\bibliography{GFL.bib}
\bibliographystyle{unsrt}
\nocite{*}
\end{document}
